---
title: "r_package_practice"
author: "Dahun Seo"
output: 
  rmarkdown::html_vignette:
    css: styles.css
vignette: >
  %\VignetteIndexEntry{r_package_practice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation

To install the package from GitHub with vignette support:

```{r, eval = FALSE}
devtools::install_github("downey21/r_package_practice", build_vignettes = TRUE)
```

# Overview

This vignette demonstrates how to use functions in the **`r_package_practice`** package.  
The package includes:

- R functions with documentation via roxygen2
- C++ functions integrated via Rcpp
- An example dataset
- A vignette (this one!)
- Internal helper functions (not exported, but still accessible)

# R Function Examples

```{r}
library(r_package_practice)

# Multiply two matrices and scale by 10
mat1 <- matrix(1:6, nrow = 2)
mat2 <- matrix(1:6, nrow = 3)
multiply_matrix_ten_times(mat1, mat2)
```

```{r}
# Add two matrices element-wise
plus_two_matrix(
  matrix(1:4, nrow = 2),
  matrix(5:8, nrow = 2)
)
```

```{r}
# Add matrices with NA check
with_na <- matrix(c(1, NA, 3, 4), nrow = 2)
plus_two_matrix(with_na, matrix(5:8, nrow = 2))  # Will print NA position
```

# Accessing Internal Functions

Functions that are **not exported** (i.e., no `@export` in roxygen) can still be accessed using the triple-colon `:::` syntax.

```{r}
# Check for NA using internal function
mat_with_na <- matrix(c(1, NA, 5, 9), nrow = 2)
r_package_practice:::check_for_na(mat_with_na)
```

This is useful for testing or learning, though it's generally discouraged for production code.

# Using C++ Functions Directly

C++ functions defined in `src/` with `// [[Rcpp::export]]` are **automatically registered** and callable from R.

```{r}
# Use C++ function directly
mat_a <- matrix(1:4, nrow = 2)
mat_b <- matrix(5:8, nrow = 2)
prod_cpp(mat_a, mat_b)  # C++ matrix multiplication
```

```{r}
# Transpose-multiply: t(mat1) %*% mat2
t_prod_cpp(mat_a, mat_b)
```

All C++ functions with `Rcpp::export` are accessible just like any R function after loading the package.

# Example Data

The package includes a simple example dataset:

```{r}
data(example_data)
example_data
```

# Summary

This vignette covered:

- Calling R and C++ functions from the package
- Accessing internal functions via `:::`
- Working with included datasets
- Using C++ for fast numerical operations
